---
title: "Health data"
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
source('preamble.R')

suppressMessages(library(tidyverse))
library(glue)
library(stringr)
library(lubridate)
```

## Data loading

Load SQLite databases:
```{r db-load}
df.sqplite <- readRDS(file = 'data/df_sqlite.rds')

# Database init tools
library(DBI)
sqlite_make_connection <- function(path) { dbConnect(RSQLite::SQLite(), path) }

```


## Misfit

```{r misfit-import}
df.misfit <- df.sqlite %>% filter(str_detect(filename, 'a_SportsData_Iwown'))

# Use only first extraction (the other is identical)
con <- sqlite_make_connection(df.misfit$path[1])
list.tables <- dbListTables(con)
list.tables

```

### V3_sleep_data

Using only `v3_sleep_data`: pre-processing

```{r sleep-v3-preprocessing}
df.v3_sleep_data <- dbReadTable(con, 'V3_sleep_data')

# Adding some factors
df.v3_sleep_data <- df.v3_sleep_data %>% 
   mutate(sleep_type = factor(sleep_type))

# Adding time references
df.v3_sleep_data <- df.v3_sleep_data %>% 
   mutate(
      datetime_day = glue::glue('{year}-{month}-{day}') %>% ymd(),
      datetime_start = datetime_day + dminutes(start_time),
      datetime_end = datetime_day + dminutes(end_time) + ddays(ifelse(end_time < start_time, 1, 0))
   )
df.v3_sleep_data %>% head

```

### Sleep distribution

Sleep distribution w/ type, per row:
```{r sleep-segments}

df.v3_sleep_data %>% 
   filter(year == 2017) %>% 
   ggplot() + 
   geom_segment(aes(x = ID, y = datetime_start, xend = ID, yend = datetime_end, col = sleep_type), lwd = 2)
```

Guess: 

- `sleep_type = 5`: awake
- `sleep_type = 2`: not awake

Sleep characteristics:

```{r}
df.v3_sleep_data %>% 
   group_by(datetime_day, sleep_type) %>% 
   mutate(duration_segment = datetime_end - datetime_start) %>% 
   summarize(total_duration = sum(duration_segment)) %>% 
   filter(year(datetime_day) == 2017) %>%
   ggplot() +
   geom_col(aes(x = as.character(datetime_day), y = total_duration / dhours(1), fill = factor(sleep_type)), 
            position = 'dodge') +
   labs(x = 'Date', y = 'Duration [h]') + coord_cartesian(ylim = c(0, 12), expand = FALSE)
   
```



## Prometheus

Locate the DB(s):

```{r prometheus-find}
df.prometheus <- df.sqlite %>% filter(str_detect(filename, 'Prometheus'))
nrow(df.prometheus)

```

### Difference between extractions

Let's analyze first `ZS2ACTIVITYSESSION` tables:
```{r prometheus-init}
# Open connections
con.left <- sqlite_make_connection(df.prometheus$path[1])
con.right <- sqlite_make_connection(df.prometheus$path[2])
df.prometheus.act.left <- dbReadTable(con.left, 'ZS2ACTIVITYSESSION')
df.prometheus.act.right <- dbReadTable(con.right, 'ZS2ACTIVITYSESSION')
dbDisconnect(con.left)
dbDisconnect(con.right)

```

The extractions are different!

```{r prometheus-diff}
df.prometheus.act.left %>% dim
df.prometheus.act.right %>% dim

df.prometheus.act.right %>% colnames() %>% setdiff(df.prometheus.act.left %>% colnames())

```

Common contents:

```{r prometheus-diff-show}
diff.prometheus <- all_equal(
   df.prometheus.act.left %>% as.tibble() %>% select(-ZREQUESTCHANGEDVALUES), 
   df.prometheus.act.right %>% as.tibble() %>% select(one_of(colnames(df.prometheus.act.left)), -ZREQUESTCHANGEDVALUES),
   ignore_row_order = TRUE, ignore_col_order = TRUE, conver = TRUE
)
diff.prometheus

# "Rows in x but not y: 51, 53, 50, 52, 49. Rows in y but not x: 58, 59, 60, 57, 61. "

idx.unique.left <- c(51, 53, 50, 52, 49)
idx.unique.right <- c(58, 59, 60, 57, 61)
df.prometheus.act.left %>% as.tibble() %>% select(-ZREQUESTCHANGEDVALUES)
```

Notice: same DB, only PK changes!

### Activities

We consider only `df.prometheus.act.left`.    
It should contain step data.

A brief summary:
```{r}
df.prometheus.act.left %>% head
```

Some pre-processing:
```{r}
# Adding some factors
df.prometheus.act.left <- df.prometheus.act.left %>% 
   mutate(ZACTIVITYTYPE = factor(ZACTIVITYTYPE))
```



Column `ZSTARTTIME` is a timestamp, attempt to convert to time:
```{r}
df.prometheus.act.left %>% 
   mutate(datetime_start = as.POSIXct(ZSTARTTIME, origin = '1970-01-01'),
          datetime_end = datetime_start + dseconds(ZDURATION)) %>% 
   select(ZDATEYYYYMMDD, ZSTARTTIME, datetime_start, ZDURATION, datetime_end) %>% 
   head(10)
```


It seems ok! (Perhaps we need to adjust for time zones.)   
Save this:    
```{r}
df.prometheus.act.left <- df.prometheus.act.left %>% 
   mutate(datetime_start = as.POSIXct(ZSTARTTIME, origin = '1970-01-01'),
          datetime_end = datetime_start + dseconds(ZDURATION))
```



Activities:
```{r}
df.prometheus.act.left %>% 
   mutate(datetime = ZDATEYYYYMMDD %>% ymd()) %>% 
   ggplot() + 
   geom_point(aes(x = datetime, y = dseconds(ZDURATION) / dminutes(1), col = ZACTIVITYTYPE)) + 
   labs(x = 'Date', y = 'Duration [min]')
   
```

As segments:

```{r}
df.prometheus.act.left %>% 
   ggplot() +
      geom_segment(aes(x = ymd(ZDATEYYYYMMDD), 
        xend = ymd(ZDATEYYYYMMDD), 
        y = datetime_start %>% POSIX_strip(origin = '1970-01-01'), 
        yend = datetime_end %>% POSIX_strip(origin = '1970-01-01'), 
        col = ZACTIVITYTYPE), lwd = 2) +
   scale_y_datetime(date_labels = '%H:%M') +
   labs(x = 'Date', y = 'Time of the day')
```

